Supplement: Bootstrapping Domain Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-02-09 supplement.tex
consistent list type notation

\subsection{List Functions}
The lower section with seven primitives designates those given to the
\emph{rich} DSL variant and not the \emph{base} variant. The rich variant is
not supplied the \texttt{if} primitive, because its primary intention is to
enable the learning of the lower five concepts.
Greek letters represent polymorphic types.
\begin{center}
\tt
\begin{tabular}{| l | l |}
  \hline
  \textrm{\emph{name}} & \textrm{\emph{type}} \\
  \hline
    empty & [$\alpha$] \\
    singleton & $\alpha \to$ [$\alpha$] \\
    concat & [$\alpha$] $\to$ [$\alpha$] $\to$ [$\alpha$] \\
    mapi & $(\mathbb{Z} \to \alpha \to \beta)$ \\
    & \qquad\qquad$\to$ [$\alpha$] $\to$ [$\beta$] \\
    reducei & $(\beta \to \mathbb{Z} \to \alpha \to \beta)$\\
    & \qquad\qquad$\to \beta \to$ [$\alpha$] $\to \beta$ \\
    \hline
    if & bool $\to \alpha \to \alpha \to \alpha$ \\
    \hline
    true & bool \\
    not & bool $\to$ bool \\
%UNUSED+UNNECESSARY:    and & bool $\to$ bool $\to$ bool \\
%UNUSED+UNNECESSARY:    or & bool $\to$ bool $\to$ bool \\
    0 $\cdots$ 5 & $\mathbb{Z}$ \\
    + & $\mathbb{Z} \to \mathbb{Z} \to \mathbb{Z}$ \\
    * & $\mathbb{Z} \to \mathbb{Z} \to \mathbb{Z}$ \\
    negate & $\mathbb{Z} \to \mathbb{Z}$ \\
    mod & $\mathbb{Z} \to \mathbb{Z} \to \mathbb{Z}$ \\
    eq? & $\mathbb{Z} \to \mathbb{Z} \to$ bool \\
    gt? & $\mathbb{Z} \to \mathbb{Z} \to$ bool \\
    is-prime & $\mathbb{Z} \to$ bool \\
    is-square & $\mathbb{Z} \to$ bool \\
    range & $\mathbb{Z} \to$ [$\mathbb{Z}$] \\
    sort & [$\mathbb{Z}$] $\to$ [$\mathbb{Z}$] \\
    \hline
    sum & [$\mathbb{Z}$] $\to \mathbb{Z}$ \\
    reverse & [$\alpha$] $\to$ [$\alpha$] \\
    all & $(\alpha \to$ bool$) \to$ [$\alpha$] $\to$ bool \\
    any & $(\alpha \to$ bool$) \to$ [$\alpha$] $\to$ bool \\
    index & $\mathbb{Z} \to$ [$\alpha$] $\to \alpha$ \\
    filter & $(\alpha \to$ bool$) \to$ [$\alpha$] $\to$ [$\alpha$] \\
    slice & $\mathbb{Z} \to \mathbb{Z} \to$ [$\alpha$] $\to$ [$\alpha$] \\
  \hline
\end{tabular}
\end{center}

>>>>

\subsection{List Functions}
The lower section with seven primitives designates those given to the
\emph{rich} DSL variant and not the \emph{base} variant. The rich variant is
not supplied the \texttt{if} primitive, because its primary intention is to
enable the learning of the lower five concepts.
Greek letters represent polymorphic types.
\begin{center}
\tt
\begin{tabular}{| l | l |}
  \hline
  \textrm{\emph{name}} & \textrm{\emph{type}} \\
  \hline
    empty & $\left[\alpha\right]$ \\
    singleton & $\alpha \to \left[\alpha\right]$ \\
    concat & $\left[\alpha\right] \to \left[\alpha\right] \to \left[\alpha\right]$ \\
    mapi & $(\mathbb{Z} \to \alpha \to \beta)$ \\
    & \qquad\qquad$\to \left[\alpha\right] \to \left[\beta\right]$ \\
    reducei & $(\beta \to \mathbb{Z} \to \alpha \to \beta)$\\
    & \qquad\qquad$\to \beta \to \left[\alpha\right] \to \beta$ \\
    \hline
    if & bool $\to \alpha \to \alpha \to \alpha$ \\
    \hline
    true & bool \\
    not & bool $\to$ bool \\
%UNUSED+UNNECESSARY:    and & bool $\to$ bool $\to$ bool \\
%UNUSED+UNNECESSARY:    or & bool $\to$ bool $\to$ bool \\
    0 $\cdots$ 5 & $\mathbb{Z}$ \\
    + & $\mathbb{Z} \to \mathbb{Z} \to \mathbb{Z}$ \\
    * & $\mathbb{Z} \to \mathbb{Z} \to \mathbb{Z}$ \\
    negate & $\mathbb{Z} \to \mathbb{Z}$ \\
    mod & $\mathbb{Z} \to \mathbb{Z} \to \mathbb{Z}$ \\
    eq? & $\mathbb{Z} \to \mathbb{Z} \to$ bool \\
    gt? & $\mathbb{Z} \to \mathbb{Z} \to$ bool \\
    is-prime & $\mathbb{Z} \to$ bool \\
    is-square & $\mathbb{Z} \to$ bool \\
    range & $\mathbb{Z} \to$ [$\mathbb{Z}$] \\
    sort & $\left[\mathbb{Z}\right] \to \left[\mathbb{Z}\right]$ \\
    \hline
    sum & $\left[\mathbb{Z}\right] \to \mathbb{Z}$ \\
    reverse & $\left[\alpha\right] \to \left[\alpha\right]$ \\
    all & $(\alpha \to$ bool$) \to \left[\alpha\right] \to$ bool \\
    any & $(\alpha \to$ bool$) \to \left[\alpha\right] \to$ bool \\
    index & $\mathbb{Z} \to \left[\alpha\right] \to \alpha$ \\
    filter & $(\alpha \to$ bool$) \to \left[\alpha\right] \to \left[\alpha\right]$ \\
    slice & $\mathbb{Z} \to \mathbb{Z} \to \left[\alpha\right] \to \left[\alpha\right]$ \\
  \hline
\end{tabular}
\end{center}
